\begin{acknowledgements}
It took three years for this thesis to come out. If it is written as required, the necessary appreciation for these three years will not fit into one page. For this reason only a brief version of my gratitude is shown here.\\
First of all, I would like to thank Robert Sch\"{o}fbeck for writing this project and choosing me as his student. At every crucial point of the work, he was there and supporting with very beneficial advice. He always encouraged us to reach our best. I also would like to thank Wolfgang Adam. He was always there to discuss problems and finding solutions together. He was always managing to make us happy even in the very stressful times with his calm and positive attitude. I am also grateful to Prof. Jochen Schieck, my thesis supervisor and director of HEPHY, for providing an inspiring atmosphere within the institute.\\
Furthermore, I want to thank the other jury members, Rosy Nikolaidou and Hubert Kroha for reading this thesis.\\
Moreover, I want to thank all my colleagues at HEPHY for an efficient and at the same time friendly working atmosphere. I further appreciated support from Daniel Spitzbart, Navid k. Rad, Federico Ambrogy, Matheusz Zarucki, Erica Brondolin, Ilse Kratschmer, Johannes Brandstetter, Wolfgang Wltenberger and Suchita Kulkarni when I had a ski accident at the end of my PhD.\\
I would like to thank also my ACDVF colleagues, Claudia Seitz, Henning Kirschenmann, Anadi Canepa, Dirk Kr\"{u}cker, Stephan Lammel, Artur Lobanov, Isabell Melzer-Pellmann, Basil Schneider, Anna Stakia, Paris Sphicas and Markus Stoye for their great team work when publishing our analysis.\\
A thank you should also go to all the CMS groups, the LHC team and all the people working at CERN. \\
Moreover, thank you to our beloved IT at HEPHY, Dietrich Liko, for his patience and very talented work. He always answered our needs whenever possible including nights and weekends. I would like to thank Ren\'{e} Brun for ROOT, Guido van Rossum for Python and Bram Moolenaar for Vim.\\
A special thank you goes my flatmate Ayseg\"{u}l, my mom , my brother and his girlfriend Meltem for always providing the support that I need outside the work life.\\
Final but not least, this thesis was made possible with the FWF project P26771-N20 and Doktoratskolleg Particles and Interactions (DK-PI).

Thanks for all your encouragement!

\end{acknowledgements}
